Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-21 CMSAC_presentation/CMSAC_reveal_js.qmd
slides

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank
:::

>>>>

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
:::
